---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```{css}
/* 1. Background Styling */
body {
  background-color: #007373;
  color: white;
  line-height: 1.8;
  padding: 50px;
}

/* 2. Heading Styling */
h2 {
  color: #FFD;
  border-bottom: 5px solid gold;
  padding-left: 10px;
  text-transform: uppercase;
}

/* 3. Image Styling */
img {
  border: 3px solid #2c3e50;
  border-radius: 12px;
  box-shadow: 0px 4px 20px rgba(255,215,0,1);
  margin-bottom: 25px;
}

```

## Digital Distraction Analysis

```{r}

#Load library quietly 

suppressPackageStartupMessages(library(tidyverse))

# Define the URL of published Google Sheet CSV
# Make sure the link ends in "output=csv"

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSZP5qQEGGk6uftQRyUv8qEvgGi9C4K9RsW9wKkV9LTZ00rsKFwwGVrL8pFxm22Cmfi0V8a-tfx0Li4/pub?output=csv"

# Read the data directly from the web into a data frame called logged_data

logged_data <- read_csv(csv_url)

# Copy the EXACT rename logic from exploration.R
latest_data <- logged_data %>%
  rename(time_stamp = 1,
    app_name = 2,
    reason_notify = 3,
    recovery_time = 4,
    time_of_day = 5,
    urgency_score = 6)
```

```{r}
# Calculate all the summary value 
# 1. Calculate the average minutes lost per notification
avg_recovery <- mean(latest_data$recovery_time, na.rm = TRUE)

# 2. Find the highest urgency level logged
max_urgency <- max(latest_data$urgency_score, na.rm = TRUE)

# 3. MIN: The shortest recovery time (the "quickest" distraction)
quickest_recovery <- min(latest_data$recovery_time, na.rm = TRUE)

# 4. Total minutes lost (Sum of all recovery times)
# Shows the "big picture" of time wasted.
total_minutes_lost <- sum(latest_data$recovery_time, na.rm = TRUE)

# 5. LENGTH: Total number of observations logged
# The length of the 'app_name' column to see the count
total_observations <- length(latest_data$app_name)

```

```{r}
# Use paste0 to join my variables into a professional paragraph.
# \n creates a new line for better formatting.

dynamic_content <- paste0(
  "Notification Analysis Summary",
  "During this data collection period, I recorded a total of ", total_observations, " notifications. ",
  "On average, each interruption cost me ", round(avg_recovery, 2), " minutes of productivity. ",
  "Across all logs, I have lost a total of ", total_minutes_lost, " minutes to digital distractions.",
  "In terms of urgency, the most critical notification I received was rated a ", max_urgency, 
  " out of 10, where 1 meant not urgent and 10 meant extremely urgent, while my quickest recovery back to work took only ", quickest_recovery, " minute(s)."
)

# cat() prints the text so it looks like regular writing on your website.
cat(dynamic_content)

```

```{r}

#FINAL BAR CHARTS

# 1. Frequency of Notifications by App Source
final_plot_apps <- ggplot(latest_data, aes(x = app_name)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Frequency of Notifications by App Source",
       x = "Application",
       y = "Number of Notifications") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# Prints the first chart
final_plot_apps 


# 2. Notification Distribution Throughout the Day
final_plot_time <- ggplot(latest_data, aes(x = time_of_day)) +
  geom_bar(fill = "magenta") +
  labs(title = "Notification Distribution Throughout the Day",
       x = "Time Period",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme_minimal()

# Prints the second chart
final_plot_time 

# Primary Reasons for Interruptions 
final_plot_reason <- latest_data %>%
  mutate(reason_short = recode(reason_notify, 
                               "Academic/Coursework (Classes, announcements, assignments)" = "Academic/Coursework",
                               "Life Admin & Utility (Gaspy, banking, fitness trackers, reminders)"="Life Admin & Utility", 
                               "Entertainment (Youtube/Games)"="Entertainment",
                               "Club/Extracurricular Activity (Meeting reminders, sponsorships)" = "Club/Extracurricular",
                               "Social (Messages from friends and family)" = "Social", 
                               "Other"= "Other")) %>%
  ggplot(aes(x = reason_short)) +
  geom_bar(fill = "darkblue") +
  labs(title = "Primary Reasons for Interruptions",
       x = "Reason",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
# Keeps the labels tidy


# Prints the third chart
final_plot_reason

# Notification Urgency Distribution
final_plot_urgency <- ggplot(latest_data, aes(x = urgency_score)) +
  geom_bar(fill = "gold", color = "black") +
  labs(title = "Distribution of Urgency Scores",
       x = "Urgency Rating (1-10)",
       y = "Count") +
  theme_light()

# Prints the fourth chart
final_plot_urgency
```
